---
title: "Cocktails"
author: "oggismetto"
date: "26/05/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r}

Sys.setlocale("LC_TIME", "en_US.UTF-8")

library(tidyverse)
library(tidytuesdayR)
library(here)
library(hrbrthemes)
library(cowplot)

theme_set(theme_light())

devtools::install_github("gadenbuie/ggpomological")
scales::show_col(ggpomological:::pomological_palette)

boston_cocktails <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-05-26/boston_cocktails.csv')

```

* can be a network of drinks linked by the ingredients they share
* is it possible a cluster analysis?
* grouped in macrocategories
* we can use the widyr package by Dave Robinson to correlated the cocktails based on shared ingredients
* have an excuse to study the chapter 4 of the text mining book

* can filter for all citrus stuff in drinks
* then i wander possible drinks i could try by the fruits in it

```{r}

library(igraph)
library(graphlayouts)
library(ggraph)
library(tidytext)
library(widyr)

# We may instead want to examine correlation among words, which indicates how often they appear together relative to how often they appear separately.
# we need to filter for at least relatively common words first
# drink with at least 5 ingredients

# orange based cocktails
boston_cocktails_edges <- boston_cocktails %>% 
  distinct(name, ingredient) %>%
  mutate(ingredient = tolower(ingredient)) %>%
  filter(str_detect(ingredient, c("orange|curacao|mandarine|`triple sec`"))) %>%
  filter(!str_detect(ingredient, c("wedge|twist|wheel|peel|zest"))) %>%
  left_join(boston_cocktails, by = "name") %>%
  distinct(name, ingredient.y) %>%
  rename(drink = name, ingredient = ingredient.y) %>%
  add_count(drink) %>%
  filter(n >= 4) %>% #with at least 4 ingredients
  pairwise_cor(drink,ingredient, sort = TRUE) %>%
  filter(correlation > 0.5) %>%
  rename(`Correlation (links)` = correlation)

# boston cocktails nodes
boston_cocktails_nodesize <- boston_cocktails %>% 
    distinct(name, ingredient) %>%
    mutate(ingredient = tolower(ingredient)) %>%
    filter(str_detect(ingredient, c("orange|curacao|mandarine|`triple sec`"))) %>%
    filter(!str_detect(ingredient, c("wedge|twist|wheel|peel|zest"))) %>%
    left_join(boston_cocktails, by = "name") %>%
    distinct(name, ingredient.x)  %>%
    count(name, sort = T)

boston_cocktails_nodecolour <- boston_cocktails %>% 
    distinct(name, ingredient) %>%
    mutate(ingredient = tolower(ingredient)) %>%
    filter(str_detect(ingredient, c("orange|curacao|mandarine|`triple sec`"))) %>%
    filter(!str_detect(ingredient, c("wedge|twist|wheel|peel|zest"))) %>%
    left_join(boston_cocktails, by = "name") %>%
    distinct(name, ingredient.x) %>%
    group_by(name) %>%
    filter(row_number() == 1)

boston_cocktails_node_attributes <- boston_cocktails_nodesize %>%
    inner_join(boston_cocktails_nodecolour) %>%
  merge(boston_cocktails_edges, by.x = "name", by.y = "item1", all.y =  TRUE) %>%
  distinct(name, n, ingredient.x) %>%
  rename(favourite_ingredient = ingredient.x) %>%
  mutate(favourite_ingredient = str_replace(favourite_ingredient, "juice of orange", "orange juice"),
         favourite_ingredient = str_replace(favourite_ingredient, "^orange$", "fresh orange juice"),
         favourite_ingredient = str_replace(favourite_ingredient, "^each orange juice and sweet sherry$", "fresh orange juice"))

# network
net <- graph_from_data_frame(d=boston_cocktails_edges, vertices=boston_cocktails_node_attributes, directed=F) 
lay = create_layout(net, layout = "fr")

# Plot
orange_plot <- ggraph(lay) +
  geom_edge_link(aes(edge_color = `Correlation (links)`)) +
  geom_node_point(aes(color = favourite_ingredient)) +
  geom_node_text(aes(label = name), repel = TRUE) +
  scale_edge_color_continuous(low = "grey", high = "black") +
  labs(title = "My \"to drink\" list: drinks with my favourite fruit, guess which one!",
       subtitle = "Correlation between orange based drinks based on their shared ingredients",
       color = "Orange based drinks (nodes)",
       caption = "by @GoldenB16117397 | source: #TidyTuesday/Kaggle & Kaggle | Cocktails") +
  theme_void() + 
  scale_color_pomological() +
  theme(
  plot.margin = unit(rep(1, 4), "cm"),
  plot.title = element_text(size = 18, 
                            face = "bold",
                            color = "#22292F", 
                            margin = margin(b = 8)),
  plot.subtitle = element_text(size = 14, 
                               lineheight = 1.1,
                               color = "#22292F",
                               margin = margin(b = 25)),
  plot.caption = element_text(size = 10,
                              margin = margin(t = 25), 
                              color = "#3D4852"),
  plot.background = element_rect(fill = "#fffeea", color = NA), 
  panel.grid = element_blank())

orange_plot <- ggdraw() +
  draw_plot(orange_plot) +
    draw_image("https://lh3.googleusercontent.com/proxy/9LkPjN3LQXuqWgFaFbVJUumGUOudx370BdLqkQRSOQU5e9ucQQ4md8hG01yziuqqV40LwF_j_UGqHsVjKEqiHLD4edo8oKO6IqRcSdZohGhzSn8X-Lw", x = 0.37, y = 0.32, scale = .2)

png(here("plots","2020_22", "cocktails.png"), 
    width = 12, height = 7, units = 'in', res = 300)
orange_plot
dev.off()

```

