---
title: "Volleyball"
author: "oggismetto"
date: "20/05/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r}

Sys.setlocale("LC_TIME", "en_US.UTF-8")

library(tidyverse)
library(patchwork)
library(hrbrthemes)
library(tidytuesdayR)
library(here)

tuesdata <- tidytuesdayR::tt_load(2020, week = 21)
volley <- tuesdata$vb_matches %>%
    mutate(match_id = row_number())


```

* im gonna train with pivot_longer to long format this table
* gonna count the players in the world
* can be a network of players who played together and how many victories / defeats?
* this is biased by the huge number of brazilian players i bet
* im gonna show relative numbers to avoid confounding

```{r}

volley_long <- volley %>%
  rename(w_p1_name = w_player1, w_p2_name = w_player2,
         l_p1_name = l_player1, l_p2_name = l_player2) %>%
mutate_at(vars(starts_with("w_"), starts_with("l_")), as.character) %>%
  pivot_longer(cols = c(starts_with("w_"), starts_with("l_"))) %>%
  separate(name, c("winner_loser", "player", "name"),
           sep = "_",
           extra = "merge",
           fill = "right") %>%
  mutate(winner_loser = str_to_upper(winner_loser))
  
volley_players  <- volley_long %>%
  filter(name != "rank") %>% 
  spread(name, value) %>%
  select(name, country, gender)

```

Pair stats

```{r}

  
losers <-  volley %>%
    select(gender, match_id, l_player1, l_player2, l_p1_country, l_p2_country) %>%
    mutate(label = "losers") %>%
  rename(player1 = l_player1, player2 = l_player2,
         country1 = l_p1_country, country2 = l_p2_country)

winners <-  volley %>%
    select(gender, match_id, w_player1, w_player2, w_p1_country, w_p2_country) %>%
    mutate(label = "winners") %>%
  rename(player1 = w_player1, player2 = w_player2,
         country1 = w_p1_country, country2 = w_p2_country)

by_pairs <- rbind(losers, winners) %>%
    select(-match_id) %>%
    count(player1, player2, label, country1, country2, gender) %>%
    spread(label, n) %>%
  filter(losers + winners > 100) %>%
  mutate(ratio_wins = winners/(winners + losers))

```

Single Winner stats (filter for the genes in the pairs)
```{r}

winners <-volley %>%
    pivot_longer(cols = c(w_player1, w_player2),  
                 names_to = "Player", 
                 values_to = "Name") %>%
  select(Player, Name) %>%
  count(Name, sort = T)

losers <-volley %>%
    pivot_longer(cols = c(l_player1, l_player2),  
                 names_to = "Player", 
                 values_to = "Name") %>%
  select(Player, Name) %>%
  count(Name, sort = T)

winner_stats <- winners %>%
    merge(losers, by = "Name") %>%
    rename(n_wins = n.x, n_loss = n.y) %>%
    mutate(n_matches = n_wins + n_loss,
           ratio_wins = n_wins/n_matches) %>%
    arrange(desc(ratio_wins)) %>%
  filter(n_matches > 100)

winner_stats <- 
  merge (winner_stats, volley_players, by.x = "Name", by.y = "name", all.x = TRUE) %>%
  distinct()

```

* lets learn how to use ggraph

```{r}

library("igraph")
library("graphlayouts")
library("ggraph")

# https://kateto.net/network-visualization

by_pairs %>%
  count(country2, sort = T)

links2 <- by_pairs %>%
  filter(country1 == c("United States")) %>%
  mutate(ratio_wins = ratio_wins * 100) %>%
  select(player1, player2, ratio_wins, gender, country1) %>%
  rename(from = player1, to = player2, `Pair winning rate (%)` = ratio_wins, country = country1)

uno <- links2 %>%
  select(from) %>%
  rename(player = from)

due <- links2 %>%
  select(to) %>%
  rename(player = to)

link_nodes <- rbind(uno, due)

nodes2 <- winner_stats %>%
    select(Name, ratio_wins, gender, country) %>%
  merge(link_nodes, by.x = "Name", by.y = "player", all.y = TRUE) %>%
  distinct()

#net <- graph_from_data_frame(d=links2 %>% filter(gender == "M"), 
#                             vertices=nodes2 %>% filter(gender == "M"), directed=F) 
#
net <- graph_from_data_frame(d=links2, vertices=nodes2, directed=F) 

# ggraph
# http://users.dimi.uniud.it/~massimo.franceschet/ns/syllabus/make/ggraph/ggraph.html

lay = create_layout(net, layout = "fr")

# New facet label names for dose variable
facet_labs <- c("Men connect with a density of 4.27%", "Women connect with a density of 3.53%")
names(facet_labs) <- c("M", "W")

bvolley <- ggraph(lay) + 
    geom_edge_link(aes(edge_color= `Pair winning rate (%)`), edge_width = 2) + 
    geom_node_text(aes(label = name), repel=TRUE)+ 
    geom_node_point(aes(color = gender, size = ratio_wins * 100)) +
    theme_graph() +
  facet_nodes(~gender, nrow = 3, ncol = 2, labeller = labeller(gender = facet_labs)) + 
    th_foreground(foreground = 'grey', border = TRUE) +
  labs(title = "American beach volleyball players, how much do they connect?",
      subtitle = "Network of players and their winning rates in pairs and as individuals", 
       size = "Single player\nwinning rate (%)",
       colour = "Gender",
       caption = "by @GoldenB16117397 | source: #TidyTuesday/BigTimeStats | Beach Volleyball")

png(here("plots","2020_21", "beach_volleyball.png"), 
    width = 14, height = 8, units = 'in', res = 300)
bvolley
dev.off()


# learn with igraph
plot(net,
     vertex.size = (V(net)$ratio_wins*2)^4, 
     edge.width = (E(net)$weight * 2)^4)

plot(net)

```

* new idea, analyse general connectivity between man and women of the same state
* top 3 countries per number of players

density analysis
```{r}

# Brazil - M
PC = 17*16/2 = 136
AC = 15
density = 15/136 = 0.1102941

# US - M
PC = 41*40/2 = 820
AC = 35
density = 35/820 = 0.04268293

# Brazil - W
PC = 19*18/2 = 171
AC = 16
density = 16/171 = 0.09356725

# US - W
PC = 45*44/2 = 990
AC = 35
density = 35/990 = 0.03535354

# check the stats

# Germany - M
PC = 16*15/2 = 120
AC = 12
density = 12/120 = 0.1

# Germany - W
PC = 25*24/2 = 300
AC = 14
density = 14/300 = 0.04666667

```


